Parallel Global Search Algorithm with Local Tuning\\ for Solving Mixed-Integer Global Optimization Problems

### 2021-02-18 2021/Lobachevskii_BarkalovLebedev/ljmsamp.tex
Fix list of references

\bibitem{Gaviano}
M.~Gaviano, D.~Lera, D.~E.~Kvasov and Ya.~D.~Sergeyev, \textit{Software for generation of classes of test functions with known local and global minima for global optimization}, ACM Trans. Math. Softw. \textbf{29}, 469--480 (2003).

>>>>

\bibitem{Gaviano}
M.~Gaviano, D.~Lera, D.~E.~Kvasov and Y.~D.~Sergeyev, \textit{Software for generation of classes of test functions with known local and global minima for global optimization}, ACM Trans. Math. Softw. \textbf{29}, 469--480 (2003).
